Seg_sites_rarefaction

### 2024-10-01 scripts/seg_sites_rarefaction.Rmd
minor fixes, added line numbers to response

ggsave("Figure1.pdf", f1, width = 15, height = 10)
tapply(F1data[F1data$source == "Mathematical", "in_ci"], F1data[F1data$source == "Mathematical", c("K", "pop")], mean) # percent in interval
```

>>>>

ggsave("Figure1.pdf", f1, width = 15, height = 10)
tapply(F1data[F1data$source == "Mathematical", "in_ci"], F1data[F1data$source == "Mathematical", c("K", "pop")], function(x) mean(ifelse(x == "Yes", TRUE, FALSE))) # percent in interval
mean(ifelse(F1data[F1data$source == "Mathematical", "in_ci"] == "Yes", TRUE, FALSE))
```
